Flesh Simulation in the Field of Animation

### 2019-12-05 LaTeX-Master-Vorlage/chapter/Background.tex
small adjustments

\[
\mathbb{A}=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right] 
=\boldsymbol{\check{A}}.
\]

@@

\section{Continuum Mechanics}
In this section I will give a broad introduction into the field of Continuum Mechanics. In Continuum Mechanics one is less interested in small particles like atoms or molecules of an object but rather in pieces of matter which are in comparison very large. I are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p. 1).

@@

\subsubsection{Polar Decomposition of the Deformation Gradient}
With the help of mathematics one can decompose the deformation gradient in the following form:

\[
\mathbf{F} = \mathbf{RS}
\]

@@

In the context of flesh simulations I use the poisson's ratio as a characterization for the resistance to volume change of flesh. Biological tissues such as flesh, fat and muscles have one important property: Volume preservation. As a result the poisson's ratio is a higher value, meaning it is found in the range between 0.45 and 0.5 \cite{Smith:2018:SNF:3191713.3180491}.

The calculation of the poisson's ratio defined in equation \ref{eq:poisson} is a challenge. Fortunately we can make use of the \textit{Lamé Parameters}. These are the two constants $\mu$ and $\lambda$ that are specific for a material. With the help of these two constants one can transform the equation \ref{eq:poisson} into the following form:

\begin{equation}\label{eq:poisson_ratio}
\sigma =  \frac{\lambda}{2(\lambda + \mu)}
\end{equation}

>>>>

\[
\mathbb{A}=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right] 
=\mathbf{\check{A}}.
\]

@@

\section{Continuum Mechanics}
In this section I will give a broad introduction into the field of Continuum Mechanics. In Continuum Mechanics one is less interested in small particles like atoms or molecules of an object but rather in pieces of matter which are in comparison very large. I am therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p. 1).

@@

\subsubsection{Polar Decomposition of the Deformation Gradient}
With the help of theorem \ref{PD} one can decompose the deformation gradient in the following form:

\[
\mathbf{F} = \mathbf{RS}.
\]

@@

In the context of flesh simulations I am using the poisson's ratio as a characterization for the resistance to volume change of flesh. Biological tissues such as flesh, fat and muscles have one important property: Volume preservation. As a result the poisson's ratio is a higher value, meaning it is found in the range between 0.45 and 0.5 \cite{Smith:2018:SNF:3191713.3180491}.

The calculation of the poisson's ratio defined in equation \ref{eq:poisson} is a challenge. Fortunately we can make use of the \textit{Lamé Parameters}. These are the two constants $\mu$ and $\lambda$ that are specific for a material. With the help of these two constants one can transform equation \ref{eq:poisson} into the following form:

\begin{equation}\label{eq:poisson_ratio}
\sigma =  \frac{\lambda}{2(\lambda + \mu)}.
\end{equation}

### 2019-12-05 LaTeX-Master-Vorlage/chapter/paper.tex
small adjustments

\subsection{Stability}
The core goal of the paper was to model deformations for virtual characters that have human-like features. They concentrated on the deformation energy. In order to achieve a convincing result as a first step we need to specify some requirements. For our needs in this case the stability of the energy is important. More precisely we need a hyperelastic energy that is stable in the following four important ways:

\textbf{1. Inversion Stability:} Given some arbitrary object it is possible that while deforming the object we can arrive at a zero volume state or even an entire inversion. Take for example the tetrahedron shown in figure \ref{fig:inversion_1}. In figure \ref{fig:inversion_2} we see a deformed state of this tetrahedron where the volume is scaled down to zero and we are left with a simple triangle. In figure \ref{fig:inversion_3} image we have an inversion of the object. The needed deformation energy has to be able to deal with both cases. That means that the energy has to be singularity-free and does not need any filters or threshold (\cite{Smith:2018:SNF:3191713.3180491}, 12:3).

@@

\textbf{2. Reflection stability:} A reflection is rotation around the coordinate origin.
For the deformation energy we need it to be well behaved regardless of the reflection convention used in the singular value decomposition.

@@

\todoredefined[inline]{
TODO: Finish reflection stability. Maybe add own images? Some more sources?
}

@@

In previous literature a few energies were proposed that should be analysed properly.

@@

\todoredefined[inline]{
TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources. Overall okay?
}

@@

\todoredefined[inline]{
TODO: Load into OpenFlipper and screenshot results. Include more examples and what went right and what went wrong.
}

>>>>

\subsection{Stability}
The core goal of the paper was to model deformations for virtual characters that have human-like features. They concentrated on the deformation energy. In order to achieve a convincing result the first step is to specify some requirements. For our needs in this case the stability of the energy is important. More precisely we need a hyperelastic energy that is stable in the following four important ways:

\textbf{1. Inversion Stability:} Given some arbitrary object it is possible that while deforming the object one can arrive at a zero volume state or even an entire inversion. Take for example the tetrahedron shown in figure \ref{fig:inversion_1}. In figure \ref{fig:inversion_2} we see a deformed state of this tetrahedron where the volume is scaled down to zero and we are left with a simple triangle. In figure \ref{fig:inversion_3} image we have an inversion of the object. The needed deformation energy has to be able to deal with both cases. That means that the energy has to be singularity-free and does not need any filters or threshold (\cite{Smith:2018:SNF:3191713.3180491}, 12:3).

@@

\textbf{2. Reflection stability:} A reflection is rotation around the coordinate origin. The deformation energy needs to be well behaved regardless of the reflection convention used in the singular value decomposition.

@@

\todoredefined[inline]{
TODO: Finish reflection stability. Maybe add own images and more sources. Improve English in this section.
}

@@

In previous literature a few energies were proposed that should be analysed properly. They are listed in table \ref{table:energies} below.

@@

\todoredefined[inline]{
TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources. Improve English sentences. Overall okay concerning the content?
}

@@

\todoredefined[inline]{
TODO: Load into OpenFlipper and screenshot results. Include remaining examples (diff. lamé param. and changes in method) and what went right and what went wrong.
}
